Who introduced this bug? \\ It may not have been caused by the previous commit!

### 2016-04-05 paperICSME.tex
añadiendo comentarios sobre related work

\gema{Añadir algunas referencias que nos comentaron los revisores: (Kamei et al., "A Large-Scale Empirical Study of Just-in-Time Quality Assurance," TSE 2013
Tan et al., "Online Defect Prediction for Imbalanced Data," ICSE SEIP 2015
Tantithamthavorn et al., "The Impact of Mislabelling on the Performance and Interpretation of Defect Prediction Models," ICSE 2015)}

@@

\gema{En la discussion podemos poner tambien una pequeña lista con los casos mas repetidos en los que el commit previo no es responsable: He revisado esos casos y he obtenido la siguiente lista:
- Cambios en la APi\\
- Cambios en el nombre de una variable\\
- Cambios en el formato, pero no son FP, si no que despues del cambio la funcion hace lo mismo que antes, por ejemplo guardan valores de retorno de funciones en variables y usan esa variable en vez de la llamada de la función directamente, o \\
- Lineas eliminando 'imports' que no se usan \\
- Evolución del lenguaje ó código ya que antes no podía soportar ciertas cosas como por ejemplo traducciones y ahora si, por tanto los tickets hablan de fallos en la traduccion y en realidad no habia traduccion porque probablemente en el momento de insertar el código no se soportaba. \\
- Errores gramaticales arrastrados de commit previos.
- Actualizaciones de SO, requisitos, etc.
}
\section{Threats to validity}
\label{sec:threats}

>>>>

\gema{Añadir algunas referencias que nos comentaron los revisores: (Kamei et al., "A Large-Scale Empirical Study of Just-in-Time Quality Assurance," TSE 2013
Tan et al., "Online Defect Prediction for Imbalanced Data," ICSE SEIP 2015
Tantithamthavorn et al., "The Impact of Mislabelling on the Performance and Interpretation of Defect Prediction Models," ICSE 2015)}
\gema{A brief summary about "A Large-Scale Empirical Study of Just-in-Time Quality Assurance": In this paper the concept of 'Just-in Time Quality Assurance' is presented, this concept focus in identifying defect-prone at level of software changes/patches instead of files or packages, this way the developers can review these risky changes while they are still fresh in their minds. In the paper they present as change risk model in which several characteristics of a software changes are implemented(lines added, developer experience...) They want provide an effort-reducing way to focus on the most risky changes, they empirically evaluated their approach in "Just-In-Time Quality Assurance" to identify in real time software changes that would be a defect}

\gema{A brief summary about "The Impact of Mislabelling on the Performance and Interpretation of Defect Prediction Models": In the paper the authors carried out a study where investigated the nature of mislabelled issue reports and also how this mislabelled impact in the prediction models. Finding that the mislabelling is not random. Furthermore the models trained using data noise are often just as accurate as the ones trained with clear data, but using clear data will likely allow the models to identify more of the truly defective modules. }

\gema{{A brief summary about "Online Defect Prediction for Imbalanced Data":  }

@@

\gema{En la discussion podemos poner tambien una pequeña lista con los casos mas repetidos en los que el commit previo no es responsable: He revisado esos casos y he obtenido la siguiente lista:
- Cambios en la APi\\
- Cambios en el nombre de una variable\\
- Cambios en el formato, pero no son FP, si no que despues del cambio la funcion hace lo mismo que antes, por ejemplo guardan valores de retorno de funciones en variables y usan esa variable en vez de la llamada de la función directamente, o \\
- Lineas eliminando 'imports' que no se usan \\
- Evolución del lenguaje ó código ya que antes no podía soportar ciertas cosas como por ejemplo traducciones y ahora si, por tanto los tickets hablan de fallos en la traduccion y en realidad no habia traduccion porque probablemente en el momento de insertar el código no se soportaba. \\
- Errores gramaticales arrastrados de commit previos.
- Actualizaciones de SO, requisitos, etc.
}

\gema{Defect models which identify defect-prone software models  could improve their recall and precision predicting defect-prones modules whereas they have into account our study[1, "An Extensive Comparison of Bug Prediction Approaches", 17, 27, 33, 34, 36, "BugCache for Inspections: Hit or Miss?", “Predicting Defects for Eclipse,”]}
\section{Threats to validity}
\label{sec:threats}
